---
title: "Problem Set 8"
output: html_document
---

Name: 

We will continue to work with the electrofish data for problem set 8 - file "2013 PR Tributory Electrofishing Data.csv"
NOTE: To help with rendering the Rmd, please:
1) Make sure that the data and file are saved in the same folder
2) Make sure that you have included code to load necessary packages and to import the data within the .Rmd script


### 1) Data import
NOTE: This should be directly copied from your work on Monday.
Read in the data and store it as a tibble with strings as characters.
Re-adjust data to by the correct data types.


```{r}

```


### 2) Length and width
Plot the relationship between length and weight for the most common species.
Please label the axes appropriately (units are mm) and provide a descriptive title.
Please adjust the axis text to make it larger.
Q: How will you identify the most common species?
Q: What geom will you use?
```{r}

```


### 3) Differences between species
TASK: Plot a comparison of the lengths of the different fish species.
Please label the axes appropriately (units are mm) and provide a descriptive title.
Please adjust the axis text to make it larger.
Q: What geom will you use?
```{r}

```


### 4) Species composition
Species (cols) x location (rows) matrices are commonly used for analyzing species diversity (think: the "wide" version of the Moorea dataset). For this dataframe, treat tributaries as locations.
Create a species x location matrix where the entries are the number of individuals of that species observed in the location.
```{r}

```


### Species relationships
Using your new dataframe from 6, plot the relationship between WCT and BKT abundances
Please label the axes appropriately and provide a descriptive title.
```{r}

```

