---
title: "Problem Set 5"
output: html_document
---


## 1) SPECIES RICHNESS WITH N-DEPOSITION 
Check out  http://www.cedarcreek.umn.edu/research/experiments/e001

#### i)  What did Clark and Tilman 2008 find? See text and Figure 1  
Q: What pattern did they observe between species richness and nitrogen treatment?  
Q: What years and treatments did they include in Figure 1?  


###WORKFLOW: Mimic Figure 1 (except on the y-axis just plot species richness).
Metadata here: http://www.cedarcreek.umn.edu/research/data/dataset?ple001  

#### ii) With a partner, write out the workflow you will use in English and put up a green sticky when done.
**Data QAQC**
To clean the data, I will first remove any biomass values that are NA or are less than or equal to zero.
Second, I will remove any species entries that are not species (e.g., miscellaneous categories, etc). To identify these values I will look at the unique species values, and then filter out the entries that do not correspond to actual species.
Third, to make sure that species are not double counted I will only retain unique values for each field/plot/year/treatment/species combination. To do this I will remove the biomass column and retain unique entries. 

**Data manipulation**
I will calculate species richness within each field/plot/year/treatment combination. I will group the data by field, plot, year, and treatment and count the number of rows within each group to measure species richness.
Second, I will calculate the mean and std error of richness within each treatment and year.
Third, I will filter the data to only retain the first 25 years (following Clark and Tilman 2008), and to only retain a control, low, medium, and high N treatment.


#### iii) After we have discussed as a class, write out and run the workflow in tidyverse R.
Here's the data import to get you going:
```{r}
# load the tidyverse package
library(tidyverse)

# create a function to calculate standard error
calcSE<-function(x){
  x <- x[is.na(x)==F]
  sd(x)/sqrt(length(x))
}

# read in the data 
cdrplant <- read.csv("e001_Plant aboveground biomass data.csv", stringsAsFactors = F, skip = 726) %>%
  as_tibble()

cdrrich <- cdrplant %>%
  
  # remove entries with no biomass
  filter(!is.na(Biomass), Biomass > 0) %>%
  
  # remove entries that are not species option 1, this is one way that is faster with many species
  filter(!Species %in% c("Miscelaneous Woody", "Miscelanious herb", "Pine cones", "Mosses & lichens 2", "Miscellaneous forb", "Miscellaneous sedges", "Miscellaneous woody plants", "Miscellaneous grasses 2", "Miscellaneous legumes", "Forb seedlings", "Miscellaneous rushes", "Fungi", "Miscellaneous grasses", "Miscellaneous sp.", "Miscellaneous herbs", "Miscellaneous litter")) %>%
  
  # remove entries that are not species option 2, this is the way we learned, but it is tedious with many species...
  # here just removing two entries as a demo
  filter(Species != "Miscellaneous litter",
         Species != "Miscellaneous herbs") %>%
  
  # select only unique species 
  select(Year, Field, Plot, NTrt, Species) %>%
  unique() %>%
  
  # calculate richness within year, field, plot and treatment
  group_by(Year, Field, Plot, NTrt) %>%
  summarize(rich=n()) %>%
  
  # calculate mean richness and se richness within year and treatment
  group_by(Year,NTrt) %>%
  summarize(avg_rich = mean(rich), se_rich = calcSE(rich)) %>%

  # select only the years and treatments that Clark and Tilman 2008 used
  # choosing to use just the first control treatment here (1 and not 9)
  # Not that you can use the %in% syntax such that: NTrt %in% c(1,2,3,5)
  filter(Year < 2005,
         NTrt == 1 | NTrt == 2 | NTrt == 3 | NTrt == 5) 
  

ggplot(cdrrich, aes(x=Year,y=avg_rich,color=as.factor(NTrt)))+geom_point() + geom_line() + geom_errorbar(aes(x=Year,ymin=avg_rich-se_rich,ymax=avg_rich+se_rich))

```



## 2) TOTAL BIOMASS WITH OVER TIME 
Check out  http://www.cedarcreek.umn.edu/research/experiments/e001

#### i) What did Haddad et al. 2002 find? See text and Figure 6  
- What happened to total biomass during the drought?  
- What years, treatments and fields did they include in Figure 6a?

### WORKFLOW A: Mimic Figure 6a. Please make a graph of mean total biomass in the successional field control plots over time. Include standard errors around each plotted point. 

Metadata here: http://www.cedarcreek.umn.edu/research/data/dataset?ple001

#### ii) Write out the workflow you will use in English.
- What QAQC will you do beforehand? What data will you include and what will you drop?  
- How will you manipulate the data to create the graph?  


#### iii) Write out and run the workflow in tidyverse R.
Please comment your code. Here's the data import to get you going:
```{r}
cdrplant <- read.csv("e001_Plant aboveground biomass data.csv", stringsAsFactors = F, skip = 726) %>%
  as_tibble() 
```


## 3) C:N RATIOS WITH N-DEPOSITION
Check out  http://www.cedarcreek.umn.edu/research/experiments/e001  

#### i) What did Wedin and Tilman 1996 find? See text and Figure 7  

### WORKFLOW: Please make a graph of the ratio of C:N in aboveground biomass in response to the amount of nitrogen added by species. Include standard error bars around each plotted point.
Unlike Wedin, these data are just from Field C, so no need to represent each field separately.  
The sample sizes for some species and N levels are very low, please only include species that have at least 4 replicates in each of at least 3 nitrogen levels.  NOTE: It is okay to iteratively check this (e.g., plotting first and then identifying which species match these criteria)
Metadata here: http://www.cedarcreek.umn.edu/research/data/dataset?nbe001

#### ii) Write out the workflow you will use in English.
- What QAQC will you do beforehand?  
- How will you manipulate the data to create the graph?  


#### iii) Write out and run the workflow in tidyverse R.  
Please comment your code. Here's the data import to get you going:
```{r}
cdrCN <- read.csv("e001_Plant aboveground biomass carbon and nitrogen.csv", stringsAsFactors = F, skip = 491) %>%
  as_tibble()
```

*QUESTION: How does aboveground tissue C:N ratios change with N enrichment? Do patterns appear consistent across species?*
