---
title: "Problem Set 5"
output: html_document
---


## 1) SPECIES RICHNESS WITH N-DEPOSITION 
Check out  http://www.cedarcreek.umn.edu/research/experiments/e001

#### i)  What did Clark and Tilman 2008 find? See text and Figure 1  
Q: What pattern did they observe between species richness and nitrogen treatment?  
Q: What years and treatments did they include in Figure 1?  


###WORKFLOW: Mimic Figure 1 (except on the y-axis just plot species richness).
Metadata here: http://www.cedarcreek.umn.edu/research/data/dataset?ple001  

#### ii) With a partner, write out the workflow you will use in English and put up a green sticky when done.
- What QAQC will you do beforehand?
- How will you manipulate the data once you are happy with it?  

#### iii) After we have discussed as a class, write out and run the workflow in tidyverse R.
Here's the data import to get you going:
```{r}
cdrplant <- read.csv("e001_Plant aboveground biomass data.csv", stringsAsFactors = F, skip = 726) %>%
  as.tibble()
```



## 2) C:N RATIOS WITH N-DEPOSITION
Check out  http://www.cedarcreek.umn.edu/research/experiments/e001  

#### i) What did Wedin and Tilman 1996 find? See text and Figure 7  

### WORKFLOW: Mimic a panel in Figure 7 for C:N ratio of above ground biomass with nitrogen addition level
Metadata here: http://www.cedarcreek.umn.edu/research/data/dataset?nbe001

#### ii) With a partner, write out the workflow you will use in English and put up a green sticky when you are done.  
- What QAQC will you do beforehand?  
- How will you manipulate the data once you are happy with it?  


#### iii) After we have discussed as a class, write out and run the workflow in tidyverse R.  
BONUS: Please also make a panel graph of C:N by nitrogen addition for each species.  

Here's the data import to get you going:
```{r}
cdrCN <- read.csv("e001_Plant aboveground biomass carbon and nitrogen.csv", stringsAsFactors = F, skip = 491) %>%
  as.tibble()
```



## 3) TOTAL BIOMASS WITH OVER TIME AND WITH RICHNESS AND NITROGEN
Check out  http://www.cedarcreek.umn.edu/research/experiments/e001
#### i) What did Haddad et al. 2002 find? See text and Figure 6  
- What pattern did they observe between species richness and nitrogen treatment?  
-  What years and treatments did they include in Figure 1?

### WORKFLOW A: Mimic Figure 6a
Metadata here: http://www.cedarcreek.umn.edu/research/data/dataset?ple001

#### ii) With a partner (if you like), write out the workflow you will use in English.
- What QAQC will you do beforehand?  
- How will you manipulate the data once you are happy with it?  


#### iii) Write out and run the workflow in tidyverse R.

Here's the data import to get you going:
```{r}
cdrplant <- read.csv("e001_Plant aboveground biomass data.csv", stringsAsFactors = F, skip = 726) %>%
  as.tibble()
```


### WORKFLOW B: How do you hypothesize that biomass will change with nitrogen and species richness?
Metadata here: http://www.cedarcreek.umn.edu/research/data/dataset?ple001

#### iv) With a partner (if you like), write out the workflow you will use in English.  
- What QAQC will you do beforehand?  
- How will you manipulate the data once you are happy with it?  


#### v) Write out and run the workflow in tidyverse R.

Here's the data import to get you going:
```{r}
cdrplant <- read.csv("e001_Plant aboveground biomass data.csv", stringsAsFactors = F, skip = 726) %>%
  as.tibble()
```

